# Welcome! {.unnumbered}
## A template to write books ready for self-publishing

```{r, eval = FALSE}
library(formatR)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = r)
```

```{r, eval = F}
a very long line of R code that wraps in html, epub and PDF! In a pdf especially this is needed
```

```{r}

data(mtcars)
lm(mpg ~ ., data = mtcars)

```

This is how you can show verbatim code chunks in the output. This is using
a `{verbatim}` chunk (check the source `index.qmd`):

````{verbatim}
```{r}
a very long line of R code that wraps in html, epub and PDF! In a pdf especially this is needed
```
````

If you want to show the triple backticks inline, you can also do so, like this:
```` ```{r} ```` to start an R chunk and ```` ``` ```` to end it. Check the source.

## Figures

Use `knitr::include_graphics()` to include images. Check the source for how to add
labels and captions:

```{r}
#| label: fig-gosling
#| fig-cap: "Ryan Gosling looking angry."

```

See @fig-gosling for a meme.
